---
title: 'iSpatial: Cortex'
author: "Chao"
date: "3/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# iSpatail Tutorial

---

### Load package
Install iSpatial package from Github. iSpatial is based on Seurat, you need install [Seurat](https://satijalab.org/seurat/articles/install.html) first .
```{r setup}
# install iSpatial package
# devtools::install_github("Czh3/iSpatial")

# load
library(iSpatial)

library(Seurat)
library(ggplot2)
```

### Load data
Load scRNA-seq and STARmap of Mouse Cortex. 
scRNA-seq is downlaod from [Allen Brain](https://portal.brain-map.org/atlases-and-data/rnaseq)
STARmap is from [Xiao et al](https://www.science.org/doi/10.1126/science.aat5691).
```{r load_data}
# scRNA-seq data
data(scRNA_VISp)

# STARmap data
data(starmap)
```

### Normalize data
The data need be log normalized.
```{r normalize}
# scRNA-seq data
scRNA_VISp = NormalizeData(scRNA_VISp, verbose = FALSE)

# merFISH data
starmap = NormalizeData(starmap, verbose = FALSE)
```

### infer transcriptome-wide spatial expression
```{r infer, warning=FALSE}
# infer spatial transcriptome
starmap_iSpatial = iSpatial::infer(starmap, scRNA_VISp)
```


### Example of spatial expression 
Gene "Acbd7" is not in the merFISH targeted genes
```{r Acbd7}
"Acbd7" %in% rownames(NA_merFISH)
```
